Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-08-23 article/draft.tex
few typos in YT section about flags

To further study the assignment of information panels to videos, we compiled a list of $171$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information. We collected the information panels, when present, in each video by connecting to a US server and scraping the content of the web page. Four types of information panels were found in the list of visited videos as shown in figure \ref{fig9}:  information about Climate change, COVID-19 Vaccine, COVID-19 and US elections.\footnote{See: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{youtube.com/watch?v=OwqIy8Ikv-c}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{youtube.com/watch?v=9sW0OmzcmL0}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{youtube.com/watch?v=usyQgPU-VrI} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{youtube.com/watch?v=8PAwc8nlE\_Q}. Last accessed on  21/07/2021.  }
%\footnote{The links of the YouTube videos where the information panel appeared are the following: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{youtube.com/watch?v=OwqIy8Ikv-c}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{youtube.com/watch?v=9sW0OmzcmL0}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{youtube.com/watch?v=usyQgPU-VrI} and \href{https://www.youtube.com/watch?v=8PAwc8nlE_Q}{youtube.com/watch?v=8PAwc8nlE_Q}.  }

@@

For climate change we found that most of the videos ($13$ out of $18$) did not display an information panel. Lastly, no information panels were found in the general health category set, that included videos that were not related to COVID-19 but contained misinformation concerning cures for cancer, abortion, and viruses. Therefore, it is likely that YouTube add information panels below videos concerning controversial topics that can have misleading information like the climate change, COVID-19, flat earth and vaccine. It appears as if YouTube is focusing its efforts on the current ``hot'' topics with a wide public impact (elections, COVID), leaving room for misinformation to spread concerning other topics.

>>>>

To further study the assignment of information panels to videos, we compiled a list of $171$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information. We collected the information panels, when present, in each video by connecting to a US server and scraping the content of the web page. Four types of information panels were found in the list of visited videos as shown in figure \ref{fig9}:  information about Climate change, COVID-19 Vaccine, COVID-19 and US elections.\footnote{See: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{youtube.com/watch?v=OwqIy8Ikv-c}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{youtube.com/watch?v=9sW0OmzcmL0}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{youtube.com/} \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{/watch?v=usyQgPU-VrI} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{youtube.com/watch?v=8PAwc8nlE\_Q}. Last accessed on  21/07/2021.  }
%\footnote{The links of the YouTube videos where the information panel appeared are the following: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{youtube.com/watch?v=OwqIy8Ikv-c}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{youtube.com/watch?v=9sW0OmzcmL0}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{youtube.com/watch?v=usyQgPU-VrI} and \href{https://www.youtube.com/watch?v=8PAwc8nlE_Q}{youtube.com/watch?v=8PAwc8nlE_Q}.  }

@@

For climate change we found that most of the videos ($13$ out of $18$) did not display an information panel. Lastly, no information panels were found in the general health category set, that included videos that were not related to COVID-19 but contained misinformation concerning cures for cancer, abortion, and viruses. 
Therefore, it is likely that YouTube adds information panels below videos including controversial topics and that can contain misleading information like the climate change, COVID-19 and vaccines. 
It seems that YouTube is focusing its efforts on current ``hot'' topics with a potentially wide public impact (e.g. elections, COVID-19), leaving room for misinformation related to other topics to spread.
